---
title: "Create Master LAS Database"
output:
  
  html_document:
    theme: paper
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false

---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"images/logo.jpg\" style=\"position:absolute; top:0; right:0; padding:0px; height:160px\"></div>');
  $('#header').css('margin-right', '100px')
});
```

```{=html}
<style type="text/css">
div.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

Laramie Angler Survey
Last updadted: 3/22/2024
Colt Webb

Goal: Load the Raw or Cleaned data into R and look through the data to better understand what I am working with. Once cleaned and I have added any fields that I might need, write this to a geodatabase. 



```{r message=FALSE, warning=FALSE, include=FALSE}
#==============================================================================#
#      Load Packages, working path, and EPSG codes ####
#==============================================================================#
require(sf)
require(mapview)
require(maptools)
require(kableExtra)
require(tidyverse)

# My working path
myPath <- "C:/Users/colwebb/Documents/LaramieAnglerSurvey"

#Transform coordinates to Albers 
albers.usa <- 5070
```


#  {.tabset}

# Clean, fix missing data, find/avg duplicates, evaluate LicType vs. ResidenceState

## Read in data and clean

-  Any blanks or periods become NA (NA = Did Not SEE Question)

-  Keep -99 as they saw the question but did not answer

-  Assign a unique id to each row (1:4400) named SurveyID

-  Create state, county, and zip columns to use for mapping later. State is from the residence address State. County is from IT. Zip code is from the "ZipCode_Final" that Stephen manually pick the best Zip code to use. Using the zip code they entered if possible, but using the residence zip code as a replacement when necessary. He will also fix the 4 digit zip codes and trim the extra -#### from the end so that we have one column with the best reliable zip codes. 

-  Reorganize the columns so that Customer Info like name, email, address, Fee and License type come before the answers to questions

```{r echo=FALSE}
#==============================================================================#
#      Read and Clean  Data ####
#==============================================================================#
# Read in the data and fix NA
orginal <- data.frame(read.csv(paste0(myPath,"/Data/AnglerSurvey2023CleanedFile.csv"),                
                         na.strings = c(""," ",".")))  %>% # Any blanks or periods become NA (NA = Did Not SEE Question)
     # Assign a unique id to each row
     mutate(SurveyID = 1:4400) %>%   # add unique survey id number to each row 
  
     # Create the Final state and zip that I will use (I used Residence...not mail)
     mutate(state = residencestate,
            zipcode = residencezip) %>%  # Use ZipCode_Final (Stephen is going to manually pick the best Zip code to use)
  
     # Fix data types for each column
     mutate(SurveyID = as.character(SurveyID),
            customerid = as.character(customerid),
            mailzip = as.character(mailzip),
            residencezip = as.character(residencezip),
            licensetype = as.character(licensetype)) %>% 
     # Reorder the columns
     select(SurveyID,customerid, RecipientLastName:ExternalReference, mailcity:residencezip, 
            ZipCode_Entered, ZipCode_Final, state, county, zipcode, feetype, licensetype, Section1Q1:GenFacilities2)

d <- orginal


d %>% 
  select(SurveyID:licensetype) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")
```

<br>

<br>

## Determine how many surveys reponses are missing Customer Info

- 18 rows of missing info. How did this happen? 

- Might be able to State and County to those you did provide a zip code

```{r echo=FALSE}
missingInfo <- d %>% filter(is.na(customerid))

missingInfo %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")



```

<br>

<br>

## Add state and county to 16/18 "missing people" that provided their zipcode

- Manually added state and county to the 16/18 "missing people" that provided the zipcode

- I removed those survyes with missing data from the maindata frame. Then added the corrected ones back to it. 

```{r echo=FALSE}
missingInfo_corrected <- missingInfo %>%
            mutate(zipcode = ifelse(is.na(zipcode), ZipCode_Entered, zipcode)) %>%
            mutate(state = case_when(zipcode %in% c("82009", "82073" , "82070", "82072", "82331","82007" ) ~ "WY",
                                     zipcode %in% c("84655") ~ "UT")) %>% 
            mutate(county = case_when(zipcode %in% c("82073" , "82070", "82072")  ~ "ALBANY",
                                      zipcode %in% c("82009" , "82007") ~ "LARAMIE",
                                      zipcode %in% c("82331") ~ "CARBON"))
missingInfo_corrected %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")
# unique(missingInfo_corrected$SurveyID)


# Remove the Surveys with missing Info
d <- d %>% 
        filter(!SurveyID %in% c("9",    "10",   "11",   "617",  "625",  "626",  "627",
                                "628",  "629",  "630",  "631",  "2142", "2143", "2144",
                                "2145", "3883", "3884", "4390"))


# Add them back to the bottom of the dataframe
d <- rbind(d, missingInfo_corrected)
                 
```


## Determine if same person took the survey multiple times

- First remove the 18 rows of missing info. No way to tell if these were duplicated or not

- Find customerID that were listed more than once

- This list consists of 39 unique people that duplicated the survey (38 took it twice, 1 took it three times). This equals 79 survey reponses. Once I pick the first response from each person then I will be left with a table of 39 reponses (one per person). 

- Duplicates were write out to "/Data/duplicates_toAVG.csv" and sent to Chance K. He will go through and average the multiple response and send it back to me

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Find the people that took it more than once
dup <- d %>%  
          drop_na(customerid) %>%  # remove the 18 rows of missing info
          mutate(duplicate = duplicated(customerid)) %>%  # add column of TRUE or FALSE whether customerID is a duplicated 
          filter(duplicate == TRUE) %>% # pick only the customerID that were indicated being duplicated
          arrange(RecipientLastName) # arrange rows by alphabetical order of Last Name

#length(unique(dup$customerid)) # Number of unique people that took survey 
# table(dup$customerid) # One person took it 3 times, 38 took it twice



# Make dataframe of only the people that took it more than once (expect 79 rows)
# unique(dup$customerid)
dup <- d %>% 
          filter(customerid %in% c(
                   "418333",  "1349069", "11791",  "113130",  "418100",  "981794", "1678981", "1719911",
                   "633667",  "382588",  "466059",  "253024",  "595007",  "932627",  "823563",  "1080687",
                   "26017",   "601625",  "220593",  "590472",  "2467926", "1813362", "629384",  "13456",  
                   "304229",  "1427740", "160233",  "2598127", "54706",   "601067",  "853886",  "229220", 
                   "819062",  "1322892", "422200",  "524786",  "351070",  "1399009", "2616485")) %>% 
          arrange(customerid) # arrange rows by alphabetical order of Last Name


dup %>% 
  select(SurveyID:licensetype) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

write.csv(dup, paste0(myPath,"/Data/duplicates_toAVG.csv" ))

#unique(dup$SurveyID)
```

<br> 

<br>

## Remove the 79 Surveys that were one of the 39 people that took survey muliple times

```{r echo=FALSE}
d <- d %>% 
          filter(!customerid %in% c(
                   "418333",  "1349069", "11791",  "113130",  "418100",  "981794", "1678981", "1719911",
                   "633667",  "382588",  "466059",  "253024",  "595007",  "932627",  "823563",  "1080687",
                   "26017",   "601625",  "220593",  "590472",  "2467926", "1813362", "629384",  "13456",  
                   "304229",  "1427740", "160233",  "2598127", "54706",   "601067",  "853886",  "229220", 
                   "819062",  "1322892", "422200",  "524786",  "351070",  "1399009", "2616485"))
```



## Read in the the average survey scores and rbind them to the rest of the dataframe.

- I read in the file Chance K send me and the rbind it to the rest of data

```{r echo=FALSE}

# avg_duplicates <- read.csv()

# test <- rbind(d, avg_duplicates)
```



## Summmarys of License Type not matching the Residence State Info

<br>

### Resident License 

- Of the the Resident License (licensetype = 1) there are 12 that have another State listed as their residence. 

- 10/12 have a feetype as NFA, while 2 have RFA

```{r echo=FALSE}
res <- d %>% 
          filter(licensetype == "1")

unique(res$state)
table(res$state, useNA = "always")

resLic_stateNotWY <- res %>% filter(!state == "WY")

resLic_stateNotWY %>% 
select(SurveyID:licensetype) %>%
kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

```

- Table of those that listed having a resident license but do not have their residence state in WY

<br>

### Non-Resident License 

- Of the the Non-Resident License (licensetype = 2) there are 73 that have WY as their residence state, but listed a non-resident license type

- 65/73 have a feetype as NFA, while the others are 1 PBSGF, 1RFA, 1RFA and RFD, 3 RFD, 2 NAs

```{r echo=FALSE}
nonres <- d %>% 
          filter(licensetype == "2")

unique(nonres$state)
table(nonres$state, useNA = "always")

nonresLic_stateisWY <- nonres %>% filter(state == "WY")

nonresLic_stateisWY %>% 
select(SurveyID:licensetype) %>%
kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

```

- Table of the 73 people that have WY listed as their residence state but listed a non-resident licence type






























# Test making it spatial by State, County, and Zip

```{r message=FALSE, warning=FALSE, include=FALSE}

st_layers(paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg")) # look at layers

states <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "urbnmapr_states") %>% 
          rename(state = state_abbv)
counties <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "urbnmapr_counties") %>% 
          rename(state = state_abbv, counties = county_name)

zipcode <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "zipcode") %>% 
            rename(zipcode = ZCTA5CE10)

```



## State
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(states, test, by = "state")

# Remove WY and CO
map <- spatial %>% 
          filter(!state %in% c("WY", "CO")) 
co <- spatial %>% 
          filter(state %in% c("CO"))
wy <- spatial %>% 
          filter(state %in% c("WY"))
# Plot 
ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey") +
  geom_sf_text(co, mapping = aes(label = count), 
               color = "black", size = 4) +
  geom_sf(data = wy, fill = "grey") +
  geom_sf_text(wy, mapping = aes(label = count), 
               color = "black", size = 4) 
  
 # Plot  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey", color = "white") +
  geom_sf_text(co, mapping = aes(label = count), 
               color = "black", size = 4) +
  geom_sf(data = wy, fill = "grey", color = "white") +
  geom_sf_text(wy, mapping = aes(label = count), 
               color = "black", size = 4) +
  ggthemes::theme_map()

# mapview(map, zcol = "count") + mapview(co, col.region = "darkred")
 
```



## County

- all but two surveys with a county listed is from WY. The they both have zip codes in WY for both mailing and residence but the State say CO or AR. I feel like this is an error in the custumer info database we were sent
```{r echo=FALSE, message=FALSE, warning=FALSE}

question <- d %>% filter(!is.na(county))
table(question$state, useNA = "always")
question %>% 
  filter(!state == "WY") %>% 
  kbl() %>% 
  kable_classic()
```



```{r echo=FALSE, message=FALSE, warning=FALSE}

d <- d %>% 
          mutate(counties = case_when(county == "ALBANY" ~ "Albany County",
                                      county == "LARAMIE" ~ "Laramie County",
                                      county == "PLATTE" ~ "Platte County",
                                      county == "CARBON" ~ "Carbon County",
                                      county == "GOSHEN" ~ "Goshen County"))


# Summarize data I want to portray by number of response for each county 
test <- d %>% 
          group_by(counties) %>% 
          summarise(count = n())

counties <- counties %>% filter(state == "WY") # only want counties in WY

# Join it by state 
spatial <- left_join(counties, test, by = "counties")

ggplot() +
  geom_sf(data = spatial, aes(fill = count), alpha = .5)  +
  scale_fill_viridis_c(option = "virdis") 

ggplot() +
  geom_sf(data = spatial, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  ggthemes::theme_map()

# mapview(spatial, zcol = "count")
 
```





## Zip Code

- There were ones from Alaksa and Hawaii not shown

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Summarize data I want to portray by number of response for each zipcode 
test <- d %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Plot 
ggplot() +
  geom_sf(data = spatial, aes(fill = count))  +
  scale_fill_viridis_c(option = "virdis") 

# Plot 
ggplot() +
  geom_sf(data = states, alpha = 0) +
  geom_sf(data = spatial, aes(fill = count), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") + 
  ggthemes::theme_map() +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) 



# mapview(spatial, zcol = "count") 





```







## State and Zip

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())
# Join it by state 
spatial_states <- left_join(states, test, by = "state")


# Summarize data I want to portray by number of response for each zipcode 
test <- d %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
spatial_zip <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)


# Plot 
ggplot() +
  geom_sf(data = spatial_states, alpha = .5, aes(fill = count)) +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  scale_fill_viridis_c(option = "virdis") + 
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) 


ggplot() +
  geom_sf(data = spatial_states, alpha = .5, aes(fill = count), color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  scale_fill_viridis_c(option = "virdis") + 
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()



#mapview(spatial_states, zcol = "count") + mapview(spatial_zip, col.region = "grey", alpha = 0.5)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(states, test, by = "state")

# Remove WY and CO
map <- spatial %>% 
          filter(!state %in% c("WY", "CO", "AK", "HI")) 
co <- spatial %>% 
          filter(state %in% c("CO"))
wy <- spatial %>% 
          filter(state %in% c("WY"))


  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey", color = "white") +
  geom_sf(data = wy, fill = "grey", color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()
  
  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "tomato2", color = "white") +
  geom_sf(data = wy, fill = "tomato4", color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()
  
  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "tomato2", color = "white") +
  geom_sf(data = wy, fill = "tomato4", color = "white") +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()

```





## WY and CO by Zip 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          filter(state %in% c("WY", "CO")) %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Get just the CO and WY Statelines
map <- states %>% 
          filter(state %in% c("WY", "CO")) 



 ggplot() +
  geom_sf(data = map, fill = "grey", color = "white") +
  geom_sf(data = spatial, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis")   +
  ggthemes::theme_map()

# mapview(map, col.region = "grey") + mapview(spatial, zcol = "count")
```










<br> 













# Re Create WYSAC Survey Results

- using orginal data before it was cleaned and fixed in section one so that I can compare it directly to the on Jessica did. 

```{r echo=FALSE}
#==============================================================================#
#      Read and Clean  Data ####
#==============================================================================#
# Read in the data and fix NA
orginal <- data.frame(read.csv(paste0(myPath,"/Data/AnglerSurvey2023CleanedFile.csv"),                
                         na.strings = c(""," ",".")))  %>% # Any blanks or periods become NA (NA = Did Not SEE Question)
     # Assign a unique id to each row
     mutate(SurveyID = 1:4400) %>%   # add unique survey id number to each row 
  
     # Create the Final state and zip that I will use (I used Residence...not mail)
     mutate(state = residencestate,
            zipcode = residencezip) %>%  # Use ZipCode_Final (Stephen is going to manually pick the best Zip code to use)
  
     # Fix data types for each column
     mutate(SurveyID = as.character(SurveyID),
            customerid = as.character(customerid),
            licensetype = ifelse(licensetype == "1", "Resident", licensetype),
            licensetype = ifelse(licensetype == "2", "Non-Resident", licensetype),
            mailzip = as.character(mailzip),
            residencezip = as.character(residencezip),
            licensetype = as.character(licensetype)) %>% 
     # Reorder the columns
     select(SurveyID,customerid, RecipientLastName:ExternalReference, mailcity:residencezip, 
            ZipCode_Entered, ZipCode_Final, state, county, zipcode, feetype, licensetype, Section1Q1:GenFacilities2)

d <- orginal



```




## Section 1

### License Type

Total sample size is `r nrow(d)`

```{r echo=FALSE, message=FALSE, warning=FALSE}
#table(d$feetype, useNA = "always")

valid <- d %>% filter(!licensetype == "-99" , !is.na(licensetype))
other <- d %>% filter(licensetype == "-99" | is.na(licensetype))


valid <- valid %>% 
          group_by(licensetype) %>% 
          summarise(Frequency = n(),
                    'Valid Percent' = round((Frequency/nrow(valid)*100), digits = 1)) 
valid <- valid %>% 
          add_row("licensetype" = "Total", 
                  Frequency = sum(valid$Frequency),
                  'Valid Percent' = sum(valid$Percent_Valid))

other <- other %>% 
          group_by(licensetype) %>% 
          summarise(Frequency = n(),
                    'Valid Percent' = " ") 
other <- other %>% 
          add_row(licensetype = "Total", 
                  Frequency = nrow(d),
                  'Valid Percent' = " ")

tbl <- rbind(valid, other) %>% 
        rename(" " = licensetype)


tbl %>% 
  kbl(align= c("l","c","c"),
      caption = "Table 1: License Type") %>% 
  kable_classic("striped", stripe_color = "F2F4F4",  html_font = "Times New Roman", full_width = F) %>% 
  row_spec(0, bold = T, extra_css = "border-top: 1.5px solid") %>% 
  row_spec(3, bold = T) %>% 
  row_spec(6, bold = T) 
```



### Question 1

```{r message=FALSE, warning=FALSE}
table(res$state, useNA = "always")
```

### Question 2

```{r message=FALSE, warning=FALSE}

```

### Question 3

```{r message=FALSE, warning=FALSE}

```

### Question 4 - 1

```{r message=FALSE, warning=FALSE}

```

### Question 4 - 2

```{r message=FALSE, warning=FALSE}

```


### Question 4 - 3

```{r message=FALSE, warning=FALSE}

```


### Question 4 - 4

```{r message=FALSE, warning=FALSE}

```

### Question 4 - 5

```{r message=FALSE, warning=FALSE}

```


### Question 4 - 6

```{r message=FALSE, warning=FALSE}

```


### Question 4 - 7

```{r message=FALSE, warning=FALSE}

```

### Question 4 - 8

```{r message=FALSE, warning=FALSE}

```

### Question 4 - 9

```{r message=FALSE, warning=FALSE}

```



