---
title: "Create Master LAS Database"
output:
  
  html_document:
    theme: paper
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false

---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"images/logo.jpg\" style=\"position:absolute; top:0; right:0; padding:0px; height:160px\"></div>');
  $('#header').css('margin-right', '100px')
});
```

```{=html}
<style type="text/css">
div.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

<br>

**Laramie Angler Survey**

Last updadted: 3/26/2024

Colt Webb

**Goals**: 

- 1) Load the Cleaned data from Jessica into R and look through the data to better understand what I am working with. Once cleaned and I have added any fields that I might need, write this to a geodatabase. 

- 2) Combine this survey data with spatial files and roughly map them 

- 3) Use the original (unaltered) data that WYSAC used to make their report and recreate the report they did for us to check numbers. The purpose of using the original (unaltered data) is so that I can compare the numbers of my analysis to theirs. The numbers should line up since its the same data. That will allow me to feel confident in my code and then I can copy my code to the final markdown file but run it with the finalized cleaned data that I wrote to the geodatabase in part one of this script. 

<br>


```{r message=FALSE, warning=FALSE, include=FALSE}
#==============================================================================#
#      Load Packages, working path, and EPSG codes ####
#==============================================================================#
require(sf)
require(mapview)
require(maptools)
require(kableExtra)
require(tidyverse)

# My working path
myPath <- "C:/Users/colwebb/Documents/LaramieAnglerSurvey"

#Transform coordinates to Albers 
albers.usa <- 5070
```


#  {.tabset}

## 1. Clean, fix missing data, find/avg duplicates, evaluate LicType vs. ResidenceState

### Read in data and clean

-  Any blanks or periods become NA (NA = Did Not SEE Question)

-  Keep -99 as they saw the question but did not answer

-  Assign a unique id to each row (1:4400) named SurveyID

-  Create state, county, and zip columns to use for mapping later. State is from the residence address State. County is from IT. Zip code is from the "ZipCode_Final" that Stephen manually pick the best Zip code to use. Using the zip code they entered if possible, but using the residence zip code as a replacement when necessary. He will also fix the 4 digit zip codes and trim the extra -#### from the end so that we have one column with the best reliable zip codes. 

-  Reorganize the columns so that Customer Info like name, email, address, Fee and License type come before the answers to questions

```{r echo=FALSE}
#==============================================================================#
#      Read and Clean  Data ####
#==============================================================================#
# Read in the data and fix NA
orginal <- data.frame(read.csv(paste0(myPath,"/Data/AnglerSurvey2023CleanedFile.csv"),                
                         na.strings = c(""," ",".")))  %>% # Any blanks or periods become NA (NA = Did Not SEE Question)
     # Assign a unique id to each row
     mutate(SurveyID = 1:4400) %>%   # add unique survey id number to each row 
  
     # Create the Final state and zip that I will use (I used Residence...not mail)
     mutate(state = residencestate,
            zipcode = residencezip) %>%  # Use ZipCode_Final (Stephen is going to manually pick the best Zip code to use)
  
     # Fix data types for each column
     mutate(SurveyID = as.character(SurveyID),
            customerid = as.character(customerid),
            mailzip = as.character(mailzip),
            residencezip = as.character(residencezip),
            licensetype = as.character(licensetype)) %>% 
     # Reorder the columns
     select(SurveyID,customerid, RecipientLastName:ExternalReference, mailcity:residencezip, 
            ZipCode_Entered, ZipCode_Final, state, county, zipcode, feetype, licensetype, Section1Q1:GenFacilities2)

d <- orginal


d %>% 
  select(SurveyID:licensetype) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")
```

<br>

<br>

### Determine how many surveys reponses are missing Customer Info

- 18 rows of missing info. How did this happen? 

- Might be able to State and County to those you did provide a zip code

```{r echo=FALSE}
missingInfo <- d %>% filter(is.na(customerid))

missingInfo %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")



```

<br>

<br>

### Add state and county to 16/18 "missing people" that provided their zipcode

- Manually added state and county to the 16/18 "missing people" that provided the zipcode

- I removed those survyes with missing data from the maindata frame. Then added the corrected ones back to it. 

```{r echo=FALSE}
missingInfo_corrected <- missingInfo %>%
            mutate(zipcode = ifelse(is.na(zipcode), ZipCode_Entered, zipcode)) %>%
            mutate(state = case_when(zipcode %in% c("82009", "82073" , "82070", "82072", "82331","82007" ) ~ "WY",
                                     zipcode %in% c("84655") ~ "UT")) %>% 
            mutate(county = case_when(zipcode %in% c("82073" , "82070", "82072")  ~ "ALBANY",
                                      zipcode %in% c("82009" , "82007") ~ "LARAMIE",
                                      zipcode %in% c("82331") ~ "CARBON"))
missingInfo_corrected %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")
# unique(missingInfo_corrected$SurveyID)


# Remove the Surveys with missing Info
d <- d %>% 
        filter(!SurveyID %in% c("9",    "10",   "11",   "617",  "625",  "626",  "627",
                                "628",  "629",  "630",  "631",  "2142", "2143", "2144",
                                "2145", "3883", "3884", "4390"))


# Add them back to the bottom of the dataframe
d <- rbind(d, missingInfo_corrected)
                 
```


### Determine if same person took the survey multiple times

- First remove the 18 rows of missing info. No way to tell if these were duplicated or not

- Find customerID that were listed more than once

- This list consists of 39 unique people that duplicated the survey (38 took it twice, 1 took it three times). This equals 79 survey reponses. Once I pick the first response from each person then I will be left with a table of 39 reponses (one per person). 

- Duplicates were write out to "/Data/duplicates_toAVG.csv" and sent to Chance K. He will go through and average the multiple response and send it back to me

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Find the people that took it more than once
dup <- d %>%  
          drop_na(customerid) %>%  # remove the 18 rows of missing info
          mutate(duplicate = duplicated(customerid)) %>%  # add column of TRUE or FALSE whether customerID is a duplicated 
          filter(duplicate == TRUE) %>% # pick only the customerID that were indicated being duplicated
          arrange(RecipientLastName) # arrange rows by alphabetical order of Last Name

#length(unique(dup$customerid)) # Number of unique people that took survey 
# table(dup$customerid) # One person took it 3 times, 38 took it twice



# Make dataframe of only the people that took it more than once (expect 79 rows)
# unique(dup$customerid)
dup <- d %>% 
          filter(customerid %in% c(
                   "418333",  "1349069", "11791",  "113130",  "418100",  "981794", "1678981", "1719911",
                   "633667",  "382588",  "466059",  "253024",  "595007",  "932627",  "823563",  "1080687",
                   "26017",   "601625",  "220593",  "590472",  "2467926", "1813362", "629384",  "13456",  
                   "304229",  "1427740", "160233",  "2598127", "54706",   "601067",  "853886",  "229220", 
                   "819062",  "1322892", "422200",  "524786",  "351070",  "1399009", "2616485")) %>% 
          arrange(customerid) # arrange rows by alphabetical order of Last Name


dup %>% 
  select(SurveyID:licensetype) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

write.csv(dup, paste0(myPath,"/Data/duplicates_toAVG.csv" ))

#unique(dup$SurveyID)
```

<br> 

<br>

### Remove the 79 Surveys that were one of the 39 people that took survey muliple times

```{r echo=FALSE}
d <- d %>% 
          filter(!customerid %in% c(
                   "418333",  "1349069", "11791",  "113130",  "418100",  "981794", "1678981", "1719911",
                   "633667",  "382588",  "466059",  "253024",  "595007",  "932627",  "823563",  "1080687",
                   "26017",   "601625",  "220593",  "590472",  "2467926", "1813362", "629384",  "13456",  
                   "304229",  "1427740", "160233",  "2598127", "54706",   "601067",  "853886",  "229220", 
                   "819062",  "1322892", "422200",  "524786",  "351070",  "1399009", "2616485"))
```



### Read in the the average survey scores and rbind them to the rest of the dataframe.

- I read in the file Chance K send me and the rbind it to the rest of data

```{r echo=FALSE}

# avg_duplicates <- read.csv()

# test <- rbind(d, avg_duplicates)
```



### Summmarys of License Type not matching the Residence State Info

<br>

#### Resident License 

- Of the the Resident License (licensetype = 1) there are 12 that have another State listed as their residence. 

- 10/12 have a feetype as NFA, while 2 have RFA

```{r echo=FALSE}
res <- d %>% 
          filter(licensetype == "1")

unique(res$state)
table(res$state, useNA = "always")

resLic_stateNotWY <- res %>% filter(!state == "WY")

resLic_stateNotWY %>% 
select(SurveyID:licensetype) %>%
kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

```

- Table of those that listed having a resident license but do not have their residence state in WY

<br>

#### Non-Resident License 

- Of the the Non-Resident License (licensetype = 2) there are 73 that have WY as their residence state, but listed a non-resident license type

- 65/73 have a feetype as NFA, while the others are 1 PBSGF, 1RFA, 1RFA and RFD, 3 RFD, 2 NAs

```{r echo=FALSE}
nonres <- d %>% 
          filter(licensetype == "2")

unique(nonres$state)
table(nonres$state, useNA = "always")

nonresLic_stateisWY <- nonres %>% filter(state == "WY")

nonresLic_stateisWY %>% 
select(SurveyID:licensetype) %>%
kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

```

- Table of the 73 people that have WY listed as their residence state but listed a non-resident licence type







### Make any final alterations to the data after talking with Chance and Stephen

```{r}

```



### Write to geodatabse 


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Write it out
final <- d


write.csv(final, paste0(myPath,"/Data/LaramieAnglerSurveyData_Final.csv" ))


st_write(final, 
         dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
         layer = "LaramieAnglerSurveyData_Final",  
         driver = "GPKG",     
         delete_layer = TRUE)


# Test Read it in
st_layers(paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg")) # look at layers
test <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), # read in points
                    layer = "LaramieAnglerSurveyData_Final")


```






















## 2. Test making it spatial by State, County, and Zip

```{r message=FALSE, warning=FALSE, include=FALSE}

st_layers(paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg")) # look at layers

states <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "urbnmapr_states") %>% 
          rename(state = state_abbv)
counties <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "urbnmapr_counties") %>% 
          rename(state = state_abbv, counties = county_name)

zipcode <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "zipcode") %>% 
            rename(zipcode = ZCTA5CE10)

```



### State
```{r echo=FALSE, message=FALSE, warning=FALSE}

# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(states, test, by = "state")

# Remove WY and CO
map <- spatial %>% 
          filter(!state %in% c("WY", "CO")) 
co <- spatial %>% 
          filter(state %in% c("CO"))
wy <- spatial %>% 
          filter(state %in% c("WY"))
# Plot 
ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey") +
  geom_sf_text(co, mapping = aes(label = count), 
               color = "black", size = 4) +
  geom_sf(data = wy, fill = "grey") +
  geom_sf_text(wy, mapping = aes(label = count), 
               color = "black", size = 4) 
  
 # Plot  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey", color = "white") +
  geom_sf_text(co, mapping = aes(label = count), 
               color = "black", size = 4) +
  geom_sf(data = wy, fill = "grey", color = "white") +
  geom_sf_text(wy, mapping = aes(label = count), 
               color = "black", size = 4) +
  ggthemes::theme_map()

# mapview(map, zcol = "count") + mapview(co, col.region = "darkred")
 
```



### County

- all but two surveys with a county listed is from WY. The they both have zip codes in WY for both mailing and residence but the State say CO or AR. I feel like this is an error in the customer info database we were sent
```{r echo=FALSE, message=FALSE, warning=FALSE}

question <- d %>% filter(!is.na(county))
table(question$state, useNA = "always")
question %>% 
  filter(!state == "WY") %>% 
  kbl() %>% 
  kable_classic()
```



```{r echo=FALSE, message=FALSE, warning=FALSE}

d <- d %>% 
          mutate(counties = case_when(county == "ALBANY" ~ "Albany County",
                                      county == "LARAMIE" ~ "Laramie County",
                                      county == "PLATTE" ~ "Platte County",
                                      county == "CARBON" ~ "Carbon County",
                                      county == "GOSHEN" ~ "Goshen County"))


# Summarize data I want to portray by number of response for each county 
test <- d %>% 
          group_by(counties) %>% 
          summarise(count = n())

counties <- counties %>% filter(state == "WY") # only want counties in WY

# Join it by state 
spatial <- left_join(counties, test, by = "counties")

ggplot() +
  geom_sf(data = spatial, aes(fill = count), alpha = .5)  +
  scale_fill_viridis_c(option = "virdis") 

ggplot() +
  geom_sf(data = spatial, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  ggthemes::theme_map()

# mapview(spatial, zcol = "count")
 
```





### Zip Code

- There were ones from Alaksa and Hawaii not shown

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Summarize data I want to portray by number of response for each zipcode 
test <- d %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Plot 
ggplot() +
  geom_sf(data = spatial, aes(fill = count))  +
  scale_fill_viridis_c(option = "virdis") 

# Plot 
ggplot() +
  geom_sf(data = states, alpha = 0) +
  geom_sf(data = spatial, aes(fill = count), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") + 
  ggthemes::theme_map() +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) 



# mapview(spatial, zcol = "count") 





```







### State and Zip

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())
# Join it by state 
spatial_states <- left_join(states, test, by = "state")


# Summarize data I want to portray by number of response for each zipcode 
test <- d %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
spatial_zip <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)


# Plot 
ggplot() +
  geom_sf(data = spatial_states, alpha = .5, aes(fill = count)) +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  scale_fill_viridis_c(option = "virdis") + 
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) 


ggplot() +
  geom_sf(data = spatial_states, alpha = .5, aes(fill = count), color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  scale_fill_viridis_c(option = "virdis") + 
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()



#mapview(spatial_states, zcol = "count") + mapview(spatial_zip, col.region = "grey", alpha = 0.5)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(states, test, by = "state")

# Remove WY and CO
map <- spatial %>% 
          filter(!state %in% c("WY", "CO", "AK", "HI")) 
co <- spatial %>% 
          filter(state %in% c("CO"))
wy <- spatial %>% 
          filter(state %in% c("WY"))


  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey", color = "white") +
  geom_sf(data = wy, fill = "grey", color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()
  
  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "tomato2", color = "white") +
  geom_sf(data = wy, fill = "tomato4", color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()
  
  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "tomato2", color = "white") +
  geom_sf(data = wy, fill = "tomato4", color = "white") +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) +
  ggthemes::theme_map()

```





### WY and CO by Zip 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          filter(state %in% c("WY", "CO")) %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
zip <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Get just the CO and WY Statelines and counties
state <- states %>% 
          filter(state %in% c("WY", "CO")) 
counties <- counties %>% 
          filter(state %in% c("WY", "CO")) 


 ggplot() +
  geom_sf(data = state, fill = "grey", color = "white") +
  geom_sf(data = zip, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis")   +
  ggthemes::theme_map()

# mapview(map, col.region = "grey") + mapview(spatial, zcol = "count")
```




### WY  Zip 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          filter(state %in% c("WY")) %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
zip <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Get just the CO and WY Statelines and counties
state <- states %>% 
          filter(state %in% c("WY")) 
counties <- counties %>% 
          filter(state %in% c("WY")) 


 ggplot() +
  geom_sf(data = state, fill = "grey", color = "white") +
  geom_sf(data = counties, alpha = 0, color = "black") + 
  geom_sf(data = zip, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis")   +
  ggthemes::theme_map()

# mapview(map, col.region = "grey") + mapview(spatial, zcol = "count")

mapview(counties, col.region = "grey", label = "counties") + mapview(zip, zcol = "count")
```





<br> 











