---
title: "Create Master LAS Database"
output:
  
  html_document:
    theme: paper
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false

---

```{js logo-js, echo=FALSE}
$(document).ready(function() {
  $('#header').parent().prepend('<div id=\"logo\"><img src=\"images/logo.jpg\" style=\"position:absolute; top:0; right:0; padding:0px; height:160px\"></div>');
  $('#header').css('margin-right', '100px')
});
```

```{=html}
<style type="text/css">
div.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

<br>

**Laramie Angler Survey**

Last updadted: 3/29/2024

Colt Webb

**Goals**: 

- 1) Load the Cleaned data from Jessica into R and look through the data to better understand what I am working with. Once cleaned and I have added any fields that I might need, write this to a geodatabase. 

- 2) Combine this survey data with spatial files and roughly map them 


<br>


```{r message=FALSE, warning=FALSE, include=FALSE}
#==============================================================================#
#      Load Packages, working path, and EPSG codes ####
#==============================================================================#
require(sf)
require(mapview)
require(maptools)
require(kableExtra)
require(RColorBrewer)
require(tidyverse)

# My working path
myPath <- "C:/Users/colwebb/Documents/LaramieAnglerSurvey"

#Transform coordinates to Albers 
albers.usa <- 5070
```


#  {.tabset}

## 1. Clean, fix missing data, find/avg duplicates, evaluate LicType vs. ResidenceState

### Read in data and clean

-  Any blanks or periods become NA (NA = Did Not SEE Question)

-  Keep -99 as they saw the question but did not answer

-  Assign a unique id to each row (1:4400) named SurveyID

-  Create state, county, and zip columns to use for mapping later. State is from the residence address State. County is from IT. Zip code is from the "ZipCode_Final" that Stephen manually pick the best Zip code to use. Using the zip code they entered unless: 1) they were fishing on a nonresident license (NFA) and provided a resident zip code. In that case, I pulled the residence zip code we had from the IT query, 2) typed the zip code in wrong and I was able to match it up with the residence zip code we had from IT (e.g., entered 4 digits, and I was able to get the 5th from the other column), 3) there was no entered zip code and I would default to the residence zip. A few issues Stephen noticed.. there many 4 digit zip codes that could not be corrected, resident licenses with non resident zip codes. I did not look up every single zip for every angler, so it isn't perfect, but the best that we have

- Fix data types for multiple columns making them a character rather numeric

-  Reorganize the columns so that Customer Info like name, email, address, Fee and License type come before the answers to questions

```{r echo=FALSE}
#==============================================================================#
#      Read and Clean  Data ####
#==============================================================================#
# Read in the data and fix NA
orginal <- data.frame(read.csv(paste0(myPath,"/Data/AnglerSurvey2023CleanedFile_SiddonsZipEdits.csv"),                
                         na.strings = c(""," ",".")))  %>% # Any blanks or periods become NA (NA = Did Not SEE Question)
     # Assign a unique id to each row
     mutate(SurveyID = 1:4400) %>%   # add unique survey id number to each row 
  
     # Create the Final state and zip that I will use (I used Residence...not mail)
     mutate(state = residencestate,
            zipcode = ZipCode_Final) %>%  # Use ZipCode_Final (Stephen is going to manually pick the best Zip code to use)
  
     # Fix data types for each column
     mutate(SurveyID = as.character(SurveyID),
            customerid = as.character(customerid),
            mailzip = as.character(mailzip),
            residencezip = as.character(residencezip),
            ZipCode_Entered = as.character(ZipCode_Entered),
            ZipCode_Final = as.character(ZipCode_Final),
            zipcode = as.character(zipcode),
            licensetype = as.character(licensetype)) %>% 
     # Reorder the columns
     select(SurveyID,customerid, RecipientLastName:ExternalReference, mailcity:residencezip, 
            ZipCode_Entered, ZipCode_Final, state, county, zipcode, feetype, licensetype, 
            Section1Q1:GenFacilities2) # remove cols (X, X.1, Diff)

d <- orginal


d %>% 
  select(SurveyID:licensetype) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")
```

<br>

<br>

### Determine how many surveys reponses are missing Customer Info

- 18 rows of missing info. 

```{r echo=FALSE}
missingInfo <- d %>% filter(is.na(customerid))

missingInfo %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")



```

<br>

<br>

### Remove the 18 entrys with missing customer info 

- These 18 entry ("SurveyID") were not valid responses. These were people testing the survey to see if it works.

- I removed these surveyIDs from the dataset

```{r echo=FALSE}
# the Survey ID that need to remove
unique(missingInfo$SurveyID)


# Remove the Surveys with missing Info
d <- d %>% 
        filter(!SurveyID %in% c("9",    "10",   "11",   "617",  "625",  "626",  "627",
                                "628",  "629",  "630",  "631",  "2142", "2143", "2144",
                                "2145", "3883", "3884", "4390"))

```

<br>

<br>

### Determine if same person took the survey multiple times

- Find customerID that were listed more than once

- This list consists of 39 unique people that duplicated the survey (38 took it twice, 1 took it three times). This equals 79 survey reponses. 

- Duplicates were writen out to "/Data/duplicates_toAVG.csv" and sent to Chance K. He will go through and average the multiple response and send it back to me

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Find the people that took it more than once
dup <- d %>%  
          mutate(duplicate = duplicated(customerid)) %>%  # add column of TRUE or FALSE whether customerID is a duplicated 
          filter(duplicate == TRUE) %>% # pick only the customerID that were indicated being duplicated
          arrange(RecipientLastName) # arrange rows by alphabetical order of Last Name

#length(unique(dup$customerid)) # Number of unique people that took survey  (39 uniqiue people)
# table(dup$customerid) # One person took it 3 times, 38 took it twice



# Make dataframe of only the people that took it more than once (expect 79 rows)
# unique(dup$customerid)
dup <- d %>% 
          filter(customerid %in% c(
                   "418333",  "1349069", "11791",  "113130",  "418100",  "981794", "1678981", "1719911",
                   "633667",  "382588",  "466059",  "253024",  "595007",  "932627",  "823563",  "1080687",
                   "26017",   "601625",  "220593",  "590472",  "2467926", "1813362", "629384",  "13456",  
                   "304229",  "1427740", "160233",  "2598127", "54706",   "601067",  "853886",  "229220", 
                   "819062",  "1322892", "422200",  "524786",  "351070",  "1399009", "2616485")) %>% 
          arrange(customerid) # arrange rows by alphabetical order of Last Name


dup %>% 
  select(SurveyID:licensetype) %>% 
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

write.csv(dup, paste0(myPath,"/Data/duplicates_toAVG.csv" ))

```

<br> 

<br>

###  Remove the all survey reponses from folks that took it more than once (seen in that previous table shown)

- Remove the 79 Surveys that were one of the 39 people that took survey muliple times

```{r echo=FALSE}
# the customerid that need I need to remove 
unique(dup$customerid)


# Remove the all survey reponses from folks that took it more than once
d <- d %>% 
          filter(!customerid %in% c(
                   "418333",  "1349069", "11791",  "113130",  "418100",  "981794", "1678981", "1719911",
                   "633667",  "382588",  "466059",  "253024",  "595007",  "932627",  "823563",  "1080687",
                   "26017",   "601625",  "220593",  "590472",  "2467926", "1813362", "629384",  "13456",  
                   "304229",  "1427740", "160233",  "2598127", "54706",   "601067",  "853886",  "229220", 
                   "819062",  "1322892", "422200",  "524786",  "351070",  "1399009", "2616485"))
```

<br>

<br>

### Read in the the average survey scores and rbind them to the rest of the dataframe.

- I read in the file Chance K send me and the rbind it to the rest of data

- Double check for duplicates again.....and no more duplicates exist!

```{r echo=FALSE}

# Read in data from Chance and fix data types
avg_duplicates <- data.frame(read.csv(paste0(myPath,"/Data/duplicates_AVGandRounded_byCK.csv"))) %>% 
                    
                     # Fix data types for each column
                    mutate(SurveyID = as.character(SurveyID),
                            customerid = as.character(customerid),
                            mailzip = as.character(mailzip),
                            residencezip = as.character(residencezip),
                            ZipCode_Entered = as.character(ZipCode_Entered),
                            ZipCode_Final = as.character(ZipCode_Final),
                            zipcode = as.character(zipcode),
                            licensetype = as.character(licensetype)) 
                                      
# Add these data back to the main dataset
d <- rbind(d , avg_duplicates)


# Double check for duplicates again
dup <- d %>%  
          mutate(duplicate = duplicated(customerid)) %>%  # add column of TRUE or FALSE whether customerID is a duplicated 
          filter(duplicate == TRUE) 
```

<br>

<br>


### Add Residency column that is based on the FeeType Column

- Make new col "residency" that is Resident or Non-Res by Fee Type (NFA is only non-res option). Comparing license type to fee type:

  - Licensetype= 2370 Resident, 1938 Non Resident
  - Feetype=  1999 NFA
  - resideny = 2343 Resident, 1999 Non Resident
  
  - So this mean that the number of Non Resident reponses increased by 61 people when using fee type rather than their provided answer to licensetype. Maybe this means 61 people tried to lie and purposely put they were a resident in their response when they know they were not? Or maybe it was honest mistake? Regardless, using the residency based on the fee type metric seems to be a more accurate representation. 
  

```{r echo=FALSE}
# Create Res vs NonRes based on FeeType column  
d <- d %>% 
         mutate(residency = ifelse(feetype == "NFA", "Non Resident", "Resident")) %>% # Make new col of Resident or Non-Res by Fee Type (NFA is only non-res option)
         relocate(residency, .after = licensetype)

print("licensetype")
table(d$licensetype, useNA = "always")

print("feetype")
table(d$feetype, useNA = "always")

print("residency")
table(d$residency, useNA = "always")
```

<br>

<br>




### Summmarys of License Type not matching the Residence State Info

<br>

#### Resident License 

- Of the the Resident License (residency = Resident, feetype != NFA) there are 2 that have another State listed as their residence. 

```{r echo=FALSE}
# Filter to Resident by the new residency column
res <- d %>% 
           filter(residency ==  "Resident")
          #filter(licensetype == "1")

# Table to evaluate
table(res$state, useNA = "always")


# Filter to those that are resident by state is not WY
resLic_stateNotWY <- res %>% filter(!state == "WY")

resLic_stateNotWY %>% 
select(SurveyID:licensetype) %>%
kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

```

These two folks have addresses and zipcodes in Cheyenne so I beleive that classifying them as "Resident" even though the state says otherwise is appropriate. I think the State is an error in the Custumer Info database provided by IT. Therefore, I am going to manually change these people state to WY.

##### Change the two peoples state to WY

- Now you can see that everyone that had a resident fishing license also has WY as their state

```{r echo=FALSE}
d <- d %>% 
          mutate(state = case_when(RecipientEmail == "himesbrandon66@gmail.com" ~ "WY",
                                   RecipientEmail == "flowerman91958@yahoo.com" ~ "WY",
                                   .default = as.character(state)))

# Filter to Resident by the new residency column
res <- d %>% 
           filter(residency ==  "Resident")
          #filter(licensetype == "1")

# Table to evaluate
table(res$state, useNA = "always")

```


##### Change the 6 peoples county to match their resident town

- Using the residency by fee type, we see there are 6 people with NA for the county they are from. 

```{r}

# Filter to Resident by the new residency column
res <- d %>% 
           filter(residency ==  "Resident")

# Table to evaluate 
table(res$county, useNA = "always")

#  Filter to those that are resident and NA for county info
countyNA_res <- res %>% filter(is.na(county))


# Table to view
countyNA_res %>% 
select(SurveyID:licensetype) %>%
kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")


# Correct the county info based on town
d <- d %>% 
          mutate(county = case_when(RecipientEmail == "chadsessions2@icloud.com" ~ "ALBANY",
                                    RecipientEmail == "Kufeldwr@gmail.com" ~ "ALBANY",
                                    RecipientEmail == "jeremy-mcmahon@hotmail.com" ~ "ALBANY",
                                    RecipientEmail == "COLOBOWHUNTER@YAHOO.COM" ~ "LARAMIE",
                                    RecipientEmail == "jlwright73@comcast.net" ~ "LARAMIE",
                                    RecipientEmail == "G.CREAGER0302@GMAIL.COM" ~ "LARAMIE",
                                   .default = as.character(county)))

# Filter to Resident by the new residency column
res <- d %>% 
           filter(residency ==  "Resident")

# Table to evaluate
table(res$county, useNA = "always")
table(d$county, useNA = "always")
```


<br>

#### Non-Resident License 

- Of the the Non-Resident License (residency = Non Resident, feetype = NFA) there are 107 that have WY as their residence state, but listed a non-resident residency



```{r echo=FALSE}
# Filter to Resident by the new residency column
nonres <- d %>% 
           filter(residency ==  "Non Resident")
          #filter(licensetype == "2")

# Table to evaluate
table(nonres$state, useNA = "always")  # 107 "non resident" have WY as their state


# Filter to those that are non resident but state is WY
nonresLic_stateisWY <- nonres %>% filter(state == "WY")

nonresLic_stateisWY %>% 
select(SurveyID:licensetype) %>%
kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% 
  scroll_box(width = "100%", height = "300px")

```

- Table of the 107 people that have WY listed as their residence state but had a fee type of NFA. 

- Maybe these people moved to WY recently so they have Non-resident fishing license even though they have a WY address. (I would be in this group for 2024. My address is in Laramie but my fishing license type for 2024 is NFA)

- Since these people are so new, we will count their survey response as Non Resident 

- I think these are those that are other zip codes in WY, ouside of the Laramie Region Counties



<br>

<br>




### Write to geodatabse 


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Write it out
final <- d


write.csv(final, paste0(myPath,"/Data/LaramieAnglerSurveyData_Final.csv" ))


st_write(final, 
         dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
         layer = "LaramieAnglerSurveyData_Final",  
         driver = "GPKG",     
         delete_layer = TRUE)


# Test Read it in
st_layers(paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg")) # look at layers
test <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), # read in points
                    layer = "LaramieAnglerSurveyData_Final")


```

<br>

<br>




```{r include=FALSE}
rm(list = ls(all.names = TRUE)) # Clear Environment 
```






























## 2. Test making it spatial by State, County, and Zip

- Zipcodes from Alaksa, Hawaii, and others could not be attributed with State names and therefore NAs in the state column

```{r message=FALSE, warning=FALSE, include=FALSE}
# My working path
myPath <- "C:/Users/colwebb/Documents/LaramieAnglerSurvey"

#Transform coordinates to Albers 
albers.usa <- 5070

# Read Data
st_layers(paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg")) # look at layers

states <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "urbnmapr_states") %>% 
          rename(state = state_abbv)  %>% 
          filter(!state %in% c("AK", "HI")) # Remove AK and HI

counties <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "urbnmapr_counties") %>% 
          rename(state = state_abbv, counties = county_name)

zipcode <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), 
                    layer = "zipcode")

d <- st_read(dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"), # read in points
                    layer = "LaramieAnglerSurveyData_Final")

uszip <- data.frame(read.csv(paste0(myPath,"/Data/uszip.csv"))) %>%  # https://simplemaps.com/data/us-zips
          rename(zipcode = zip) %>% 
          mutate(zipcode = as.character(zipcode))

wyzip <- uszip %>%
            filter(state_id == "WY")

wyCOzip <- uszip %>%
            filter(state_id %in% c("WY","CO"))



# I ran this to update the zipcode spatial file made from the "Create_SpatialGeoDatabaser.rmd"

## Add state to zipcode Via Spatial Join and drop the duplicates
# zipcode <- st_join(zipcode, states)
# zipcode <- zipcode %>% 
#               distinct(zipcode, .keep_all = TRUE)

## Write to GeoDatabase
# st_write(zipcode,
#          dsn = paste0(myPath, "/Data/Spatial_Data/Geodatabase/LaramieAnglerSurvey2023.gpkg"),
#          layer = "zipcode",
#          driver = "GPKG",
#          delete_layer = TRUE)


```


```{r include=FALSE}

# Formal Blue: 
"#00374D"

# Forest Green: 
"#364010"

# Sand Dunes: 
"#D8CEBA"

# Snowbank: 
"#EBEBE5"

# Meadowlark
"#FFC80B"



group.colors_WGFD <- c(Strongly_disagree = "burlywood3", 
                       Somewhat_disagree = "burlywood1",
                                 Neutral = "gray",
                          Somewhat_agree = "cadetblue3",
                          Strongly_agree = "steelblue4")

group.colors_RedGreen <- c(Strongly_disagree = "sienna4", 
                           Somewhat_disagree = "sienna3",
                                     Neutral = "gray",
                              Somewhat_agree = "darkseagreen",
                              Strongly_agree = "darkseagreen4")

```



### State

- 107 folks live in WY and mapped in WY, but are "non-resident" based on having a NFA feetype. Just be aware that these folks will show up in WY on the map. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(states, test, by = "state")

# Remove WY and CO
map <- spatial %>% 
          filter(!state %in% c("WY", "CO")) 
co <- spatial %>% 
          filter(state %in% c("CO"))
wy <- spatial %>% 
          filter(state %in% c("WY"))
# Plot 
ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey") +
  geom_sf_text(co, mapping = aes(label = count), 
               color = "black", size = 4) +
  geom_sf(data = wy, fill = "grey") +
  geom_sf_text(wy, mapping = aes(label = count), 
               color = "black", size = 4) 
  
 # Plot  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey", color = "white") +
  geom_sf_text(co, mapping = aes(label = count), 
               color = "black", size = 4) +
  geom_sf(data = wy, fill = "grey", color = "white") +
  geom_sf_text(wy, mapping = aes(label = count), 
               color = "black", size = 4) +
  ggthemes::theme_map() +
  theme(legend.position="right")

# mapview(map, zcol = "count") + mapview(co, col.region = "darkred")



  
```



### County

```{r echo=FALSE, message=FALSE, warning=FALSE}

d <- d %>% 
          mutate(counties = case_when(county == "ALBANY" ~ "Albany County",
                                      county == "LARAMIE" ~ "Laramie County",
                                      county == "PLATTE" ~ "Platte County",
                                      county == "CARBON" ~ "Carbon County",
                                      county == "GOSHEN" ~ "Goshen County"))


# Summarize data I want to portray by number of response for each county 
test <- d %>% 
          group_by(counties) %>% 
          summarise(count = n())

counties <- counties %>% filter(state == "WY") # only want counties in WY

# Join it by state 
spatial <- left_join(counties, test, by = "counties")

ggplot() +
  geom_sf(data = spatial, aes(fill = count), alpha = .5)  +
  scale_fill_viridis_c(option = "virdis") 

ggplot() +
  geom_sf(data = spatial, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  ggthemes::theme_map()+
  theme(legend.position="right")

# mapview(spatial, zcol = "count")
 
```





### Zip Code

- AK and HI did not state code from the spatial join so their state co is an NA. 

- Therefore their data is not plotted

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Summarize data I want to portray by number of response for each zipcode 
test <- d %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by zip 
spatial <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Plot 
ggplot() +
  geom_sf(data = spatial, aes(fill = count))  +
  scale_fill_viridis_c(option = "virdis") +
  theme(legend.position="right")

# Plot 
ggplot() +
  geom_sf(data = states, alpha = 0) +
  geom_sf(data = spatial, aes(fill = count), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") + 
  ggthemes::theme_map() +
  theme(legend.position="right") +
  coord_sf(xlim = c(-2361582.3,2263786.2), ylim = c(259071.7,3177425.0), expand = FALSE) 





# Remove the AK and HI zipcodes
spatial2 <- spatial %>% filter(!is.na(state))

# Plot 
ggplot() +
  geom_sf(data = states, alpha = 0) +
  geom_sf(data = spatial2, aes(fill = count))  +
  scale_fill_viridis_c(option = "virdis")  + 
  ggthemes::theme_map()+
  theme(legend.position="right")

# mapview(spatial, zcol = "count") 





```







### State and Zip

- again zip code layer for AK and HI not plotted since it was dropped due to NA

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())

# Join it by state 
spatial_states <- left_join(states, test, by = "state")


# Summarize data I want to portray by number of response for each zipcode 
test <- d %>% 
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by zip 
spatial_zip <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count) %>% 
            filter(!is.na(state))

# Plot 
ggplot() +
  geom_sf(data = spatial_states, alpha = .5, aes(fill = count)) +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  scale_fill_viridis_c(option = "virdis") +
  theme(legend.position="right")

ggplot() +
  geom_sf(data = spatial_states, alpha = .5, aes(fill = count), color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  scale_fill_viridis_c(option = "virdis") +
  ggthemes::theme_map() +
  theme(legend.position="right")



#mapview(spatial_states, zcol = "count") + mapview(spatial_zip, col.region = "grey", alpha = 0.5)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          group_by(state) %>% 
          summarise(count = n())

# Join it by state 
spatial <- left_join(states, test, by = "state")

# Remove WY and CO
map <- spatial %>% 
          filter(!state %in% c("WY", "CO", "AK", "HI")) 
co <- spatial %>% 
          filter(state %in% c("CO"))
wy <- spatial %>% 
          filter(state %in% c("WY"))


  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "grey", color = "white") +
  geom_sf(data = wy, fill = "grey", color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  ggthemes::theme_map()
  
  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "tomato2", color = "white") +
  geom_sf(data = wy, fill = "tomato4", color = "white") +
  geom_sf(data = spatial_zip, fill = "grey25", alpha = 0.2)  +
  ggthemes::theme_map()
  
  
  ggplot() +
  geom_sf(data = map, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf(data = co, fill = "tomato2", color = "white") +
  geom_sf(data = wy, fill = "tomato4", color = "white")  +
  ggthemes::theme_map()

```





### WY and CO by Zip 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          filter(zipcode %in% c(wyCOzip$zip)) %>%  # Only use zip codes from  WY
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
zip <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Get just the CO and WY Statelines and counties and zip
state <- states %>% 
          filter(state %in% c("WY", "CO")) 
counties <- counties %>% 
          filter(state %in% c("WY", "CO")) 

 ggplot() +
  geom_sf(data = state, fill = "grey", color = "white") +
  geom_sf(data = zip, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis")   +
  ggthemes::theme_map()+
  theme(legend.position="right")

# mapview(map, col.region = "grey") + mapview(spatial, zcol = "count")
```




### WY  Zip 



```{r echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data I want to portray by number of response for each state. 
test <- d %>% 
          filter(zipcode %in% c(wyzip$zip)) %>%  # Only use zip codes from  WY
          group_by(zipcode) %>% 
          summarise(count = n())

# Join it by state 
zip <- left_join(zipcode, test, by = "zipcode") %>% 
            drop_na(count)

# Get just the CO and WY Statelines and counties
state <- states %>% 
          filter(state %in% c("WY")) 
counties <- counties %>% 
          filter(state %in% c("WY")) 

 ggplot() +
  geom_sf(data = state, fill = "grey", color = "white") +
  geom_sf(data = counties, alpha = 0, color = "black") + 
  geom_sf(data = zip, aes(fill = count), alpha = .5, color = "white")  +
  scale_fill_viridis_c(option = "virdis")   +
  ggthemes::theme_map() +
  theme(legend.position="right")
  

# mapview(map, col.region = "grey") + mapview(spatial, zcol = "count")

mapview(counties, col.region = "grey", label = "counties") + mapview(zip, zcol = "count")
```



<br> 

<br> 

### Example with a speific question (Section2Q5_5: Level of agreement to manage Diamond Lake as catch and release only.)

<br>

#### State
```{r echo=FALSE, message=FALSE, warning=FALSE}
# remove NA and -99
test <- d %>%
          filter(!Section2Q5_5 == -99, !is.na(Section2Q5_5)) 

dat <- test  %>% 
          group_by(state) %>%
          summarise(count = n(),
                    mean = mean(Section2Q5_5))

 # Join it by state
 spatial <- left_join(states, dat, by = "state")

 
 # Continuous
ggplot() +
  geom_sf(data = spatial, aes(fill = mean), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf_text(spatial, mapping = aes(label = round(mean, digits = 2)),
               color = "grey30", size = 4) +
  ggtitle("Manage Diamond Lake for as catch and release only fishery (5-Strongly agree, 1- Strongly disagree)", 
          paste("Valid Reponses: ", nrow(test))) +
  ggthemes::theme_map()

ggplot() +
  geom_sf(data = spatial, aes(fill = mean), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") +
  geom_sf_text(spatial, mapping = aes(label = round(count, digits = 2)),
               color = "grey30", size = 4) +
  ggtitle("Manage Diamond Lake for as catch and release only fishery (5-Strongly agree, 1- Strongly disagree)",
          paste("Valid Reponses: ", nrow(test))) +

  ggthemes::theme_map()






# Discret
spatial <- spatial %>%
  mutate(AgreementLevel = case_when(mean > 3 ~ "Agree",
                                    mean < 3 ~ "Disagree",
                                    mean == 3 ~ "Neutral"))
ggplot() +
  geom_sf(data = spatial, aes(fill = AgreementLevel), alpha = .5,)  +
  scale_fill_manual("",
                     values=c("Agree" = "#00374D",
                              "Disagree" = "#FFC80B",
                              "Neutral" =  "#D8CEBA")) +
  geom_sf_text(spatial, mapping = aes(label = round(mean, digits = 2)),
               color = "grey30", size = 4) +
  ggtitle("Manage Diamond Lake for as catch and release only fishery (5-Strongly agree, 1- Strongly disagree)",
          paste("Valid Reponses: ", nrow(test))) +
  ggthemes::theme_map()

ggplot() +
  geom_sf(data = spatial, aes(fill = AgreementLevel), alpha = .5,)  +
  scale_fill_manual("",
                     values=c("Agree" = "#00374D",
                              "Disagree" = "#FFC80B",
                              "Neutral" =  "#D8CEBA")) +
  geom_sf_text(spatial, mapping = aes(label = round(count, digits = 2)),
               color = "grey30", size = 4) +
  ggtitle("Manage Diamond Lake for as catch and release only fishery (5-Strongly agree, 1- Strongly disagree)",
          paste("Valid Reponses: ", nrow(test))) +
  ggthemes::theme_map()





```
<br>


#### Zip
```{r echo=FALSE, message=FALSE, warning=FALSE}
# remove NA and -99
test <- d %>%
          filter(!Section2Q5_5 == -99, !is.na(Section2Q5_5)) 

dat <- test  %>% 
          group_by(zipcode) %>%
          summarise(count = n(),
                    mean = mean(Section2Q5_5))


 # Join it by state
 spatial <- left_join(zipcode, dat, by = "zipcode") %>% 
            drop_na(count)
 
 
  # Continuous
ggplot() +
  geom_sf(data = states, alpha = 0) +
  geom_sf(data = spatial, aes(fill = mean), alpha = .5,)  +
  scale_fill_viridis_c(option = "virdis") +
  ggtitle("Manage Diamond Lake for as catch and release only fishery (5-Strongly agree, 1- Strongly disagree)",
          paste("Valid Reponses: ", nrow(test))) +
  ggthemes::theme_map()






# Discret
spatial <- spatial %>%
  mutate(AgreementLevel = case_when(mean > 3 ~ "Agree",
                                    mean < 3 ~ "Disagree",
                                    mean == 3 ~ "Neutral"))
ggplot() +
  geom_sf(data = states, alpha = 0) +
  geom_sf(data = spatial, aes(fill = AgreementLevel), alpha = .5,)  +
  scale_fill_manual("",
                     values=c("Agree" = "#00374D",
                              "Disagree" = "#FFC80B",
                              "Neutral" =  "#D8CEBA")) +
  ggtitle("Manage Diamond Lake for as catch and release only fishery (5-Strongly agree, 1- Strongly disagree)",
          paste("Valid Reponses: ", nrow(test))) + 
  ggthemes::theme_map()
```



#### Zip CO and WY
```{r echo=FALSE, message=FALSE, warning=FALSE}
# remove NA and -99
test <- d %>%
          filter(!Section2Q5_5 == -99, !is.na(Section2Q5_5)) 




# Summarize data I want to portray by number of response for each state. 
dat <- test %>% 
          filter(zipcode %in% c(wyCOzip$zip)) %>%  # Only use zip codes from  WY and CO
          group_by(zipcode) %>% 
          summarise(count = n(),
                    mean = mean(Section2Q5_5))


 # Join it by state
 spatial <- left_join(zipcode, dat, by = "zipcode") %>% 
            drop_na(count)


states <- states %>% filter(state %in% c("WY", "CO"))
counties <- counties %>% filter(state %in% c("WY")) 


# Discret
spatial <- spatial %>%
  mutate(AgreementLevel = case_when(mean > 3 ~ "Agree",
                                    mean < 3 ~ "Disagree",
                                    mean == 3 ~ "Neutral"))
ggplot() +
  geom_sf(data = states, alpha = 0) +
  geom_sf(data = counties, alpha = 0, color = "black") + 
  geom_sf(data = spatial, aes(fill = AgreementLevel), alpha = .5,)  +
  scale_fill_manual("",
                     values=c("Agree" = "#00374D",
                              "Disagree" = "#FFC80B",
                              "Neutral" =  "#D8CEBA")) +
  ggtitle("Manage Diamond Lake for as catch and release only fishery (5-Strongly agree, 1- Strongly disagree)",
          paste("Valid Reponses: ", nrow(test))) + 
  ggthemes::theme_map() +
  theme(legend.position="right")

mapview(states, alpha.regions = 0) +
  mapview(counties, alpha.regions = 0) +
  mapview(spatial, zcol = "AgreementLevel")
```



